\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[margin,line]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=9.3in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Taylor Howell --- Curriculum Vitae}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\newcommand{\myname}{Taylor Howell}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \myname \vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

\input{ContactContent.tex}

% \section{\sc Citizenship}
% United States

\section{\sc Education}
{\bf Ph.D. Candidate, Mechanical Engineering,} Stanford University \hfill {\bf Sept. 2017 - present}\\
\vspace*{-.1in}
\begin{itemize}
	\item[ ] Qualifying Exams: Automatic Controls, Robotics
	\item[ ] Advisor: Zachary Manchester 
	%\item[ ] Dissertation Title: 
	%\item[ ] G.P.A.: 
\end{itemize}

{\bf M.S., Mechanical Engineering,} Stanford University \hfill {\bf June 2019}\\
\vspace*{-.1in}
\begin{itemize}
	\item[ ] Automatic Controls, Robotics
	%\item[ ] Dissertation Advisor: Dr. Zachary Manchester 
	%\item[ ] Dissertation Title: 
	%\item[ ] G.P.A.: 
\end{itemize}

{\bf B.S., Mechanical Engineering,} University of Utah \hfill {\bf Dec. 2016}\\
\vspace*{-.1in}
\begin{itemize}
\item[ ] Summa Cum Laude
%\item[ ] G.P.A.: 3.99/4.00
\end{itemize}

\section{\sc Research}
{\bf Research Assistant,} Robotic Exploration Lab, Stanford University
\hfill {\bf May 2018--Present}\\
\\
My research is focused on developing fast optimization tools for motion planning of robotic systems. Currently, I'm working on robust feedback motion planning and a fast solver for contact-implicit trajectory optimization. Previously, I was co-leading development of \texttt{TrajectoryOptimization.jl}, an open-source Julia package for solving constrained trajectory optimization problems. \\
\\
{\bf Research Assistant,} Telerobotics Laboratory, University of Utah
\hfill {\bf Oct. 2015 - Dec. 2016}\\
\\
I devised and implemented a control scheme to sort swarms of microrobots using rotating uniform
magnetic fields for minimally invasive medical applications. This work included: applied physics, simulation, nonlinear optimization, fabrication of a scaled microrobot swarm, and writing C++ code to control a tri-axial Helmholtz-coil system.\\
\\
{\bf Research Assistant,} Utah Center of Excellence for Biomedical Microfluidics, University of Utah
\hfill {\bf Sept. 2014 - Oct. 2015}\\
\\
I designed and built a forty-eight-syringe pump for a medical microfluidic system, developed standard operating procedures for a high-throughput drug screening and cytotoxicity evaluation system, and performed statistical analysis for ovarian-cancer cell experiments.\\

\section{\sc Experience}
{\bf Instructor,} GREAT Summer Camp, University of Utah
\hfill {\bf Jun. 2017 – Jul. 2017}\\
\\
Taught practical robotics and programming skills to elementary school students using the LEGO Mindstorm platform and developed projects and challenges for FLL skills, telerobotics, and kinetic-art themed weeks.\\
\\
{\bf Co-founder,} Cornaby-Howell LLC
\hfill {\bf Apr. 2015 – Oct. 2015}\\
\\
I prototyped systems including: a touch display module with GUI, Arduino C code, a lead-screw system,
and syringe attachment modules for precision high-throughput syringe pumps.\\
\\
{\bf Twisty Puzzle Designer} 
\hfill {\bf Aug. 2007 – Jan. 2011}\\
\\
I designed and built twisty puzzles with selling prices ranging from \$25 - \$850. I exhibited my work at
the community’s premier international event, Dutch Cube Day, in 2008.\\
\\

\section{\sc Publications}
1. \textbf{T. Howell}, Z. Manchester. Direct Policy Optimization. \textit{In preparation}.\\

2. B. Jackson$^*$, \textbf{T. Howell}$^*$, K. Shah, M. Schwager, Z. Manchester. Scalable Cooperative Transport of Cable-Suspended Loads with UAVs using Distributed Trajectory Optimization. 2020. Robotics and Automation Letters.\\
\\
3. \textbf{T. Howell}$^*$, B. Jackson$^*$, Z. Manchester. ALTRO: A Fast Solver for Constrained Trajectory Optimization. 2019. International Conference on Intelligent Robots and Systems. Macao, China.\\
\\
4. \textbf{T. Howell}, B. Osting, J. Abbott. Sorting Rotating Micromachines By Variations in Their Magnetic
Properties. 2018. Physical Review Applied.\\
\\
5. J. Arellano, \textbf{T. Howell}, J. Gammon, S. Cho, M. Janat Amsbury, B. Gale. Use of a highly parallel
Microfluidic Flow Cell Array to determine therapeutic drug dose response curves. 2017. Biomedical
Microdevices.\\
\\
\\
\section{\sc Skills}
Julia, C++, Python, Matlab, R\\
\LaTeX, Git, Linux, Solidworks, ROS, Adobe Premiere Pro, Adobe Illustrator \\
Mill, Lathe, Vacuum Forming, Laser Cutting, Mold Making and Casting, Metal Sheet Fabrication\\
\\
\section{\sc Coursework at Stanford}
Convex Optimization EE364a, Convex Optimization II EE364b, Optimal Control AA203, Nonlinear Control AA209, Adv. Software Development CME212, Engineering Design Optimization AA222, State Estimation AA273, Principles of Robotic Autonomy AA274, Mechatronics ME210, Linear Dynamical Systems EE263, Introduction to Robotics ME320, Machine Learning CS229, Decision Making Under Uncertainty AA228, Control Design Techniques E205, Adv. Robotic Manipulation CS326, Adv. Feedback Control AA212, Optimization MS\&E 211X, Experimental Robotics CS225a, Multi-robot Systems A277
\\

\section{\sc Fellowships and Scholarships}
Stanford Graduate Fellowship \hfill {\bf 2017 – 2018}\\
University of Utah Undergraduate Research Opportunities Program Fellowship \hfill {\bf 2016}\\
The Boeing Company Scholarship \hfill {\bf 2016}\\
Shirley L. \& Kathelyne O. Evans Endowed Scholarship \hfill {\bf 2016}\\
Big Ten+ Grad Expo travel scholarship \hfill {\bf 2016}\\
University of Utah Presidential Scholarship \hfill {\bf 2013 – 2016}
\\


\end{resume}
\end{document}
