%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\color{awesome} Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
%---------------------------------------------------------
\cventry
{Research Intern} % Affiliation/role
{Google} % Organization/group
{San Francisco, CA, USA (remote)} % Location
{June. 2021 - Sept. 2021} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item{Working on differentiable contact physics and model-predictive control for robotic manipulation.}
	\end{cvitems}
}
	
%---------------------------------------------------------
\cventry
{Course Assistant - Dynamics and Control of Aircraft (AA271a)} % Affiliation/role
{Department of Aeronautics and Astronautics, Stanford University} % Organization/group
{Stanford, CA, USA} % Location
{Apr. 2021 - Jun. 2021} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item{held office hours four times per week}
		\item{graded assignments and exams}
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Instructor - GREAT Summer Camp} % Affiliation/role
    {Department of Computer Science, University of Utah} % Organization/group
    {Salt Lake City, UT, USA} % Location
    {Jun. 2017 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {led a teaching team of three}
        \item{taught practical robotics and programming skills to elementary school students using the LEGO Mindstorm platform}
        \item {developed projects and challenges for FLL skills, telerobotics, and kinetic-art themed weeks}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder, Engineer} % Affiliation/role
    {Cornaby-Howell LLC} % Organization/group
    {Salt Lake City, UT, USA} % Location
    {Apr. 2015 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {prototyped systems: touch-display module with GUI, Arduino C code, a lead-screw system, and syringe attachment modules for precision high-throughput syringe pumps}
        \item {designed hardware schematics for patent application}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Front Desk Clerk} % Affiliation/role
    {Ramada Limited Draper} % Organization/group
    {Draper, UT, USA} % Location
    {Apr. 2013 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {manager on duty: checked in and out guests, made reservations, and ran breakfast}
        \item {developed communication and practical problem solving skills}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Twisty Puzzles} % Affiliation/role
    {Designer} % Organization/group
    {Draper, UT, USA} % Location
    {Aug. 2007 - Jan. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {designed and built twisty puzzles with selling prices ranging from \$25 - \$850}
        \item {exhibited my work at the community’s premier international event: Dutch Cube Day 2008}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
