%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\color{awesome} Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{center} \small{Lead / Co-Lead} \end{center}
\begin{cvhonors}

%---------------------------------------------------------
	\cvhonor
	{Predictive Sampling: Real-time Behaviour Synthesis with MuJoCo} % Award
	{T. Howell, N. Gileadi, S. Tunyasuvunakool, K. Zakka, T. Erez, Y. Tassa. arXiv.} % Event
	{}
	{2022} % Date(s)
	\cvhonor
	{CALIPSO: A Differentiable Solver for Trajectory Optimization with Conic and Complementarity Constraints} % Award
	{T. Howell, K. Tracy, S. Le Cleac'h. ISRR.} % Event
	{}
	{} % Date(s)
	\cvhonor
	{Dojo: A Differentiable Physics Engine for Robotics} % Award
	{T. Howell$^*$, S. Le Cleac'h$^*$, Z. Kolter, M. Schwager, Z. Manchester. arXiv.} % Event
	{}
	{} % Date(s)
   \cvhonor
	{Trajectory Optimization with Optimization-Based Dynamics} % Award
	{T. Howell, S. Le Cleac'h, S. Singh, P. Florence, Z. Manchester, V. Sindhwani. RAL.} % Event
	{}
	{2021} % Date(s)
   \cvhonor
	{Fast Contact-Implicit Model-Predictive Control} % Award
	{S. Le Cleac'h$^*$, T. Howell$^*$, M. Schwager, Z. Manchester. arXiv.} % Event
	{}
	{} % Date(s)
  \cvhonor
    {Direct Policy Optimization using Deterministic Sampling and Collocation} % Award
    {T. Howell, C. Fu, Z. Manchester. RAL.} % Event
    {}
    {} % Date(s)
    
  \cvhonor
    {Scalable Cooperative Transport of Cable-Suspended Loads with UAVs using Distributed Trajectory Optimization} % Award
    {B. Jackson$^*$, T. Howell$^*$, K. Shah, M. Schwager, Z. Manchester. RAL.} % Event
    {}
    {2020} % Date(s)
    
  \cvhonor
    {ALTRO: A Fast Solver for Constrained Trajectory Optimization}
    {T. Howell$^*$, B. Jackson$^*$, Z. Manchester. ICRA.}
    {}
    {2019}
    
  \cvhonor
    {Sorting Rotating Micromachines By Variations in Their Magnetic Properties}
    {T. Howell, B. Osting, J. Abbott. Physical Review Applied.} 
    {}
    {2018}
    
%---------------------------------------------------------
\end{cvhonors}

\begin{center} \small{Contributions} \end{center}
\begin{cvhonors}

\cvhonor 
    {RoboPianist: A Benchmark for High-Dimensional Robot Control}
    {K. Zakka, L. Smith, N. Gileadi, T. Howell, X. B. Peng, S. Singh, Y. Tassa, P. Florence, A. Zeng, P. Abbeel. arXiv.}
    {}
    {2023}
\cvhonor 
    {Differentiable Collision Detection for a Set of Convex Primitives}
    {K. Tracy, T. Howell, Z. Manchester. ICRA.}
    {}
    {}
\cvhonor
    {Differentiable Physics Simulation of Dynamics-Augmented Neural Objects}
    {S. Le Cleac'h, HX Yu, M. Guo, T. Howell, R. Gao, J. Wu, Z. Manchester, M. Schwager. arXiv.}
    {}
    {2022}
\cvhonor
    {Use of a highly parallel Microfluidic Flow Cell Array to determine therapeutic drug dose response curves}
    {J. Arellano, T. Howell, J. Gammon, S. Cho, M. Janat Amsbury, B. Gale. Biomedical Microdevices.}
    {}
    {2017}
    
\end{cvhonors}
