%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\color{awesome} Research}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Robotic Exploration Lab, Stanford University} % Organization
    {Stanford, CA, USA} % Location
    {May 2018 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      My research is focused on developing optimization-based tools for motion planning of underactuated robotic systems. Currently, I am working on algorithms for robust feedback motion planning and solvers for contact-implicit trajectory optimization. Previously, I was co-leading development of \texttt{TrajectoryOptimization.jl}, an open-source Julia package for solving constrained trajectory optimization problems.
      \end{cvitems}
    }
    
  \cventry
    {Research Assistant} % Job title
    {Telerobotics Laboratory, University of Utah} % Organization
    {Salt Lake City, UT, USA} % Location
    {Oct. 2015 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      I devised and implemented a control scheme to sort swarms of microrobots using rotating uniform magnetic fields for minimally invasive medical applications. This work included: applied physics, simulation, nonlinear optimization, fabrication of a scaled microrobot swarm, and writing C++ code to control a tri-axial Helmholtz-coil system.
      \end{cvitems}
    }
    
  \cventry
    {Research Assistant} % Job title
    {Utah Center of Excellence for Biomedical Microfluidics, University of Utah} % Organization
    {Salt Lake City, UT, USA} % Location
    {Sept. 2014 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      I designed and built a forty-eight-syringe pump for a medical microfluidic system, developed standard operating procedures for a high-throughput drug screening and cytotoxicity evaluation system, and performed statistical analysis for ovarian-cancer cell experiments.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
