\documentclass[10pt]{article}
\usepackage[margin=1.25cm, top=0.75cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{pagecolor}
\pagecolor{black}
\definecolor{lightgray}{HTML}{CCCCCC}
\color{white}
\usepackage[light, scaled=0.15]{roboto-mono}
\setmainfont{roboto-mono}
\newfontfamily\lightroboto{Roboto Mono Light}
\definecolor{linkcolor}{HTML}{ff00ff    }
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor, % Internal links
    urlcolor=linkcolor, % External links
    citecolor=linkcolor, % Citation links
    filecolor=linkcolor, % File links
}

\title{\large \textbf{Taylor A. Howell}}


\author{
    \small {website}: \href{https://thowell.github.io}{thowell.github.io} \quad\quad {email}: \href{mailto:taylor.athaniel.howell@gmail.com}{taylor.athaniel.howell@gmail.com}
}

\date{}

\begin{document}
\thispagestyle{empty} % Remove page numbering on this page
\footnotesize
\maketitle
\vspace{-1.cm}

\section*{Summary}
\noindent {\color{lightgray} I am an engineer and researcher working on high-performance robotics with expertise in numerical optimization, physics simulation, control, and machine learning.}

\section*{Education}
\textbf{PhD / MS} in \textbf{Mechanical Engineering} \hfill \textbf{September 2017 - December 2022}\\
\textbf{Dissertation}: {\color{lightgray}\it Numerical Optimization For Things That Move: Simulation, Planning, and Control}\\
\textbf{Advisors}: {\color{lightgray} Zachary Manchester, Allison Okamura}\\
\textbf{Stanford University}
\\
\\
\textbf{BS} \textit{summa cum laude} in \textbf{Mechanical Engineering} \hfill \textbf{May 2013 - December 2016}\\
\textbf{Senior Project}: {\color{lightgray} Wireless Power for Aerial Robots}\\
\textbf{University of Utah}

\section*{Professional Experience}
\textbf{DeepMind}, London, United Kingdom \hfill \textbf{June - October 2022} \\
Research Scientist Intern: \hfill Mentor: {\color{lightgray} Yuval Tassa}
\begin{itemize}
    \item {\color{lightgray}\textbf{MuJoCo MPC} (project lead) is a tool for real-time robot behavior generation using prediction control algorithms.} \\\href{https://github.com/google-deepmind/mujoco_mpc}{github.com/google-deepmind/mujoco\_mpc}
    \item {\color{lightgray} C/C++, MuJoCo, Git, numerical optimization, parallel computing, motion planning}
    \item {\color{lightgray} First author: \textit{Predictive Sampling: Real-time Behaviour Synthesis with MuJoCo}}
\end{itemize}

\noindent\textbf{Google Brain}, San Francisco, CA (remote) \hfill \textbf{June - September 2021} \\
Research Intern: \hfill Mentor: {\color{lightgray} Vikas Sindhwani}
\begin{itemize}
    \item {\color{lightgray} Python, JAX, differentiable optimization, planning algorithms}
    \item {\color{lightgray} First author: 
    \textit{Trajectory Optimization with Optimization-Based Dynamics}}
\end{itemize}

\section*{Research Experience}
\textbf{Robotic Exploration Lab}, Stanford University \hfill \textbf{May 2018 - December 2022} \\
Research Assistant: \hfill Advisor: {\color{lightgray} Prof. Zachary Manchester}
\begin{itemize}
    \item {\color{lightgray} Motion planning for drone coordination, legged locomotion, and robotic manipulation.}
    \item {\color{lightgray} Differentiable physics simulation for contact dynamics.}
    \item {\color{lightgray} Open-source software development in Julia.}
    \item{\color{lightgray} Hardware: quadrotors, quadrupeds (Stanford Doggo, Unitree A1)}
\end{itemize}

\noindent\textbf{Telerobotics Laboratory}, University of Utah \hfill \textbf{October 2015 - December 2016} \\
Undergraduate Researcher: \hfill Mentor: {\color{lightgray} Prof. Jake Abbott}
\begin{itemize}
    \item {\color{lightgray} Algorithm design for control of magnetically actuated microrobot swarms.}
    \item {\color{lightgray} Fabrication of scaled magnetic microrobot swimmers and experimentation with rotating magnetic fields.}
\end{itemize}

\noindent\textbf{Utah Center for Excellence in Biomedical Microfluidics}, University of Utah \hfill \textbf{September 2014 - October 2015} \\
Undergraduate Researcher: \hfill Mentor: {\color{lightgray} Prof. Bruce Gale}
\begin{itemize}
    \item {\color{lightgray} Design and fabrication of mechatronics device for experimental high-throughput system for testing ovarian cancer treatments.}
    \item {\color{lightgray} Assisted in experiments evaluating efficacy of cancer treatments: cell passaging, treatment preparation, tumor harvesting}
\end{itemize}

\section*{Skills}
\textbf{Programming}: {\color{lightgray} C/C++, Python, Julia}
\\
\textbf{Computational}: {\color{lightgray} \LaTeX, Git, Linux, SNOPT, Ipopt, CVX/Convex.jl, MeshCat, MuJoCo, JAX, Solidworks, VSCode, Arduino}
\\
\textbf{Fabrication}: {\color{lightgray} Mill, Lathe, Vacuum Forming, Laser Cutting, Mold Making and Casting, Metal Sheet Fabrication}

\section*{Publications}
\begin{center} \textbf{Lead | Co-Lead} \end{center}
\textit{Numerical Optimization For Things That Move: Simulation, Planning, and Control}. \textbf{T.Howell}. {\color{lightgray} Stanford University. 2022.}
[\href{https://github.com/thowell/thesis/blob/main/main.pdf}{dissertation}]
[\href{https://docs.google.com/presentation/d/1ypalKNcd1hAI59Fur3mFP5FYANqrQ1Smk2gUb-UiBIA/edit?usp=sharing}{slides}]
\\
\\
\textit{Predictive Sampling: Real-time Behaviour Synthesis with MuJoCo}. \textbf{T. Howell}{\color{lightgray}, N. Gileadi, S. Tunyasuvunakool, K. Zakka, T. Erez, Y. Tassa. arXiv. 2022.}
[\href{https://arxiv.org/abs/2212.00541}{paper}]
[\href{https://github.com/deepmind/mujoco_mpc}{code}]
\\
\\
\textit{CALIPSO: A Differentiable Solver for Trajectory Optimization with Conic and Complementarity Constraints.} \textbf{T. Howell}{\color{lightgray}, K. Tracy, S. Le Cleac'h. Z. Manchester. ISRR. 2022.}
[\href{https://arxiv.org/abs/2205.09255}{paper}]
[\href{https://github.com/thowell/CALIPSO.jl}{code}]
[\href{https://slides.com/taylorhowell/calipso}{slides}]
\\
\\
\textit{Dojo: A Differentiable Physics Engine for Robotics.} \textbf{T. Howell} {\color{lightgray}\& S. Le Cleac'h, Z. Kolter, M. Schwager, Z. Manchester. arXiv. 2022.}
[\href{https://arxiv.org/abs/2203.00806}{paper}]
[\href{https://github.com/dojo-sim}{code}]
\\
\\
\textit{Trajectory Optimization with Optimization-Based Dynamics.} \textbf{T. Howell}{\color{lightgray}, S. Le Cleac'h, S. Singh, P. Florence, Z. Manchester, V. Sindhwani. RAL. 2022.}
[\href{https://arxiv.org/abs/2109.04928}{paper}]
[\href{https://github.com/thowell/optimization_dynamics}{code}]
[\href{https://github.com/thowell/cv/blob/master/posters/optimization_dynamics_poster.pdf}{poster}]
\\
\\
\textit{Fast Contact-Implicit Model Predictive Control.} {\color{lightgray} S. Le Cleac'h \&} \textbf{T. Howell}{\color{lightgray}, M. Schwager, Z. Manchester. (submitted to TRO). 2021.}
[\href{https://arxiv.org/abs/2107.05616v2}{paper}]
[\href{https://github.com/thowell/ContactImplicitMPC.jl}{code}]
\\
\\
\textit{Direct Policy Optimization using Deterministic Sampling and Collocation.} \textbf{T. Howell}{\color{lightgray}, C. Fu, Z. Manchester. RAL. 2020.}
[\href{https://arxiv.org/abs/2010.08506v3}{paper}]
[\href{https://github.com/thowell/direct_policy_optimization}{code}]
\\
\\
\textit{Scalable Cooperative Transport of Cable-Suspended Loads with UAVs using Distributed Trajectory Optimization.} {\color{lightgray}B. Jackson \&} \textbf{T. Howell}{\color{lightgray}, K. Shah, M. Schwager, Z. Manchester. RAL. 2020.}
[\href{https://roboticexplorationlab.org/papers/distributed_quads.pdf}{paper}]
\\
\\
\textit{ALTRO: A Fast Solver for Constrained Trajectory Optimization.} \textbf{T. Howell} {\color{lightgray} \& B. Jackson, Z. Manchester. IROS. 2019.}
[\href{https://roboticexplorationlab.org/papers/altro-iros.pdf}{paper}]
[\href{https://github.com/RoboticExplorationLab/TrajectoryOptimization.jl}{code}]
\\
\\
\textit{Sorting Rotating Micromachines By Variations in Their Magnetic Properties.} \textbf{T. Howell}{\color{lightgray}, B. Osting, J. Abbott. Physical Review Applied. 2018.}
[\href{https://journals.aps.org/prapplied/pdf/10.1103/PhysRevApplied.9.054021}{paper}]
\\
\begin{center} \textbf{Contributions} \end{center}
\textit{RoboPianist: A Benchmark for High-Dimensional Robot Control.} {\color{lightgray} K. Zakka, L. Smith, N. Gileadi,} \textbf{T. Howell} {\color{lightgray}, X. B. Peng, S. Singh, Y. Tassa, P. Florence, A. Zeng, P. Abbeel. arXiv. 2023.}
[\href{https://arxiv.org/abs/2304.04150}{paper}]
\\
\\
\textit{Differentiable Physics Simulation of Dynamics-Augmented Neural Objects.} {\color{lightgray} S. Le Cleac'h, HX Yu, M. Guo, }\textbf{T. Howell}{\color{lightgray}, R. Gao, J. Wu, Z. Manchester, M. Schwager. RAL. 2022.}
[\href{https://arxiv.org/pdf/2210.09420.pdf}{paper}]
\\
\\
\textit{Differentiable Collision Detection for a Set of Convex Primitives.} {\color{lightgray} K. Tracy,} \textbf{T. Howell}{\color{lightgray}, Z. Manchester. ICRA. 2023.}
[\href{https://arxiv.org/abs/2207.00669}{paper}]
\\
\\
\textit{Use of a highly parallel Microfluidic Flow Cell Array to determine therapeutic drug dose response curves.} {\color{lightgray} J. Arellano, }\textbf{T. Howell}{\color{lightgray}, J. Gammon, S. Cho, M. Janat Amsbury, B. Gale. Biomedical Microdevices. 2017.}
[\href{https://link.springer.com/article/10.1007/s10544-017-0166-3}{paper}]

\section*{Open Source}

[\href{https://github.com/deepmind/mujoco_mpc}{MuJoCo MPC}] (lead w/ MuJoCo team @ DeepMind)
\begin{itemize}
    \item {\color{lightgray} tool for interactive robot behavior synthesis (C++)}
    \item {\color{lightgray} paid consulting work (DeepMind) for state estimation tools (C++, Python) \hfill June - September 2023}
\end{itemize}

\noindent[\href{https://github.com/thowell/CALIPSO.jl}{CALIPSO.jl}] (lead)
\begin{itemize}
\item {\color{lightgray} solver for non-convex optimization problems with conic and complementarity constraints (Julia)}
\end{itemize}

\noindent[\href{https://github.com/dojo-sim/Dojo.jl}{Dojo.jl}] (co-lead w/ S. Le Cleac'h \& J. Brüdigam)
\begin{itemize}
\item {\color{lightgray} differentiable physics engine for rigid-body dynamics with contact (Julia)}
\end{itemize}

\noindent[\href{https://github.com/RoboticExplorationLab/TrajectoryOptimization.jl}{TrajectoryOptimization.jl}] (co-lead w/ B. Jackson) 
\begin{itemize}
\item  {\color{lightgray} tool for fast trajectory optimization}
\end{itemize}
\noindent [\href{https://github.com/thowell}{github.com/thowell}]

\section*{Teaching Experience}
\textbf{Course Assistant}, Department of Aeronautics and Astronautics, Stanford University \hfill Spring 2021\\
{\color{lightgray} Dynamics and Control of Aircraft (AA271a) \hfill Prof. Stephen Rock} 
\begin{itemize}
    \item {\color{lightgray} held multiple office hours each week (virtually) and graded assignments}
\end{itemize}
\textbf{Robotics Instructor}, GREAT Summer Camp, School of Computing, University of Utah \hfill Summer 2017
\begin{itemize}
    \item {\color{lightgray} taught basic robotics and programming skills to elementary school students with LEGO Mindstormm platform}
\end{itemize}

\section*{Awards and Honors}
Stanford Graduate Fellowship \hfill  2017 - 2018
\\
\\
University of Utah Undergraduate Research Opportunities Program Fellowship \hfill 2016
\\
\\
The Boeing Company Scholarship \hfill 2016
\\
\\
Shirley L. \& Kathelyne O. Evans Endowed Scholarship \hfill 2016
\\
\\
Big Ten+ Grad Expo Travel Scholarship \hfill 2016
\\
\\
University of Utah Presidential Scholarship \hfill 2013 – 2016

\section*{Community}
\textbf{Reviewer} \hfill 2018 - 2022 \\
{\color{lightgray} ICRA, IROS, RAL} 
\\
\\
\textbf{Social Impact Night co-organizer} \hfill 2019\\
{\color{lightgray} Helped plan and run event at Stanford University to connect social-impact focused students and entrepreneurs.} 
\\
\\
\textbf{Research mentor} \hfill 2016 \\
{\color{lightgray} Mentored three summer interns at the Telerobotics Laboratory and developed soft robots with potential as catheter tips that will increase insertion distance deep in the brain and other hard-to-reach locations in the body.}
\\
\\
\textbf{Science-fair judge} \hfill 2015\\
{\color{lightgray} Surveyed projects and provided feedback to students at local elementary school in Salt Lake City.}

\section*{Coursework}
{\color{lightgray} Machine Learning · Decision Making Under Uncertainty · Deep Learning · Convex Optimization · Advanced Software Development · Optimal Control · Nonlinear Control · Engineering Design Optimization · State Estimation · Principles of Robotic Autonomy · Introduction to Mechatronics · Linear Dynamical Systems · Introduction to Robotics · Control Design Techniques · Advanced Robotic Manipulation · Advanced Feedback Control · Introduction to Optimization · Experimental Robotics · Multi-robot Systems · RL for Stochastic Control in Finance · State Space Control · Design of Experiments · Introduction to Finite Element Method · Programming for Engineers}

\end{itemize}
\end{document}